### 2023-01-31 manuscript.tex
tiny URL fonts [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/f600bf52e21065865fb4f3a0f1fb349145c9e9ce.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/f600bf52e21065865fb4f3a0f1fb349145c9e9ce/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4059272240

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/8ed1966988bc19593b6e558205553033af6267a7/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/8ed1966988bc19593b6e558205553033af6267a7}{stain/2022-fdo-paper@8ed1966}
on January 31, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/f600bf52e21065865fb4f3a0f1fb349145c9e9ce/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/f600bf52e21065865fb4f3a0f1fb349145c9e9ce}{stain/2022-fdo-paper@f600bf5}
on January 31, 2023.
